---
title: "Data 608 Assignment 1"
author: "Sung Lee"
date: "9/2/2021"
output: 
  html_document:
    code_folding: show
    df_print: paged
    toc: true
    toc_float: true
    toc_collapsed: true
    smooth_scroll: false
    toc_depth: 3
number_sections: true
theme: paper
---

** Original source for this assignment is from [https://github.com/charleyferrari/CUNY_DATA_608/blob/master/module1/hw1.rmd](https://github.com/charleyferrari/CUNY_DATA_608/blob/master/module1/hw1.rmd)


**Principles of Data Visualization and Introduction to ggplot2**

I have provided you with data about the 5,000 fastest growing companies in the US, as compiled by Inc. magazine. lets read this in:

```{r}

inc <- read.csv("https://raw.githubusercontent.com/charleyferrari/CUNY_DATA_608/master/module1/Data/inc5000_data.csv", header= TRUE)

```

And lets preview this data:

```{r}
head(inc)

```
```{r}

summary(inc)

```

Think a bit on what these summaries mean. Use the space below to add some more relevant non-visual exploratory information you think helps you understand this data:

```{r warning=FALSE}

# Insert your code here, create more chunks as necessary
library(knitr)
library(xml2)
library(dplyr)
library(summarytools)
library(psych)

# For summarytools package
opts_chunk$set(results = 'asis',      
                comment = NA,
                prompt  = FALSE,
                cache   = FALSE)

st_options(plain.ascii = FALSE,        
            style        = "rmarkdown", 
            footnote     = NA,          
            subtitle.emphasis = FALSE)  
```  

Here is a look at the frequency of the data by Industry and State.

```{r}
# Print out a frequency table of the data by Industry
freq(inc$Industry, order = "freq", plain.ascii = FALSE)

```  

Here is a look at the data by using the `psych` library. This would be looking at variables with the mean, standard deviation, et al.  

```{r}

# Growth Rate variable
describe(inc$Growth_Rate)

# Revenue variable
describe(inc$Revenue)

# Employeesvariable
describe(inc$Employees)

```  

Because of the large values for `Revenue`, it would be best to represent with log.

The following groups the data by City and State in descending order by Total Revenue in log form.

```{r warning=FALSE, message=FALSE}
inc %>%
    group_by(City, State) %>%
    summarise(totalRevenue = log(sum(Revenue))) %>%
    arrange(desc(totalRevenue))
```

## Question 1

Create a graph that shows the distribution of companies in the dataset by State (ie how many are in each state). There are a lot of States, so consider which axis you should use. This visualization is ultimately going to be consumed on a 'portrait' oriented screen (ie taller than wide), which should further guide your layout choices.


The solution below uses the `forcats` and `ggplot2` libraries. More information about `forcats` is here [https://forcats.tidyverse.org/](https://forcats.tidyverse.org/)

```{r warning=FALSE, message=FALSE}

# Answer Question 1 here

library(forcats)
library(ggplot2)
ggplot(inc, aes(x=fct_infreq(State))) + 
    geom_bar(stat="count", fill = "steelblue",  width = 0.5, position = position_dodge(width=0.3)) +
    coord_flip() +
    geom_text(aes(label=..count..), stat="count", size=3, 
              hjust=-0.2, color="black") +
    xlab("State") +
    ylab("Count") +
    theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) +
    ggtitle("The 5,000 Fastest Growing Companies in US") + 
    theme(panel.background = element_blank())


```

## Question 2

Lets dig in on the state with the 3rd most companies in the data set. Imagine you work for the state and are interested in how many people are employed by companies in different industries. Create a plot that shows the average and/or median employment by industry for companies in this state (only use cases with full data, use R's `complete.cases()` function.) In addition to this, your graph should show how variable the ranges are, and you should deal with outliers.

```{r}

# Answer Question 2 here

```

## Question 3

Now imagine you work for an investor and want to see which industries generate the most revenue per employee. Create a chart that makes this information clear. Once again, the distribution per industry should be shown.

```{r}

# Answer Question 3 here

```

